### 2020-02-27 Thesis-Chapter-Background.tex
Outline background

\section{Arguments For and Against}

@@

@@

@@

@@

@@

@@

>>>>

\section{Exceptional Access: Arguments For and Against}

@@

Primary reasons (why EA itself is beneficial):
\begin{itemize}
    \item Absolute privacy is not a right
    \item Encryption gives too much power to the individual
    \item EA would allow more crimes to be prevented and prosecuted
\end{itemize}

Secondary reasons (why studying EA is beneficial):
\begin{itemize}
    \item EA done well would be more secure and privacy preserving than EA done poorly
    \item The threat of legislative action creates urgency
\end{itemize}

@@

Primary reasons (why EA itself is bad):
\begin{itemize}
    \item Privacy is an absolute right
    \item Exceptional access gives too much power to the state
    \item Exceptional access is not possible in an acceptably secure manner
\end{itemize}

Secondary reasons (why studying EA is non-beneficial):
\begin{itemize}
    \item With both security and privacy in a poor state, research should be focused on strengthening, not weakening,
            them
    \item The technical community should not entertain delusions about what is truly possible
\end{itemize}

@@

Historical approaches and proposals out of the first crypto war that saw various amounts of support.

\begin{itemize}
    \item Clipper chip
    \item Government key escrow
    \item Oblivious key escrow \cite{goos_oblivious_1996}
    \item Partial key escrow (see \cite{denning_taxonomy_1996})
\end{itemize}

@@

Recent proposals out of the second crypto war that have various levels of support.

\begin{itemize}
    \item CLEAR \cite{ozzie_2018}
    \item Device escrow with HW \cite{savage_lawful_2018}
    \item Computational, blockchain approaches \cite{phan_key_2017}
    \item Lawful hacking \cite{nguyen_lawful_2017} \cite{soesanto_2018}
    \item Forced password disclosure \cite{bittenbender_2019}, see \cite{kerr_encryption_2017}
\end{itemize}

@@

\begin{itemize}
    \item Reject EA until technical capabilities are ready \cite{varia_2018}
    \item Be forthcoming with data so that we know what to work on \cite{armerding_2017}
    \item Don't prescribe technical methods, but be clear about principles \cite{matyas_incommensurability_2018}
    \item Fund the research \cite{varia_2018}
\end{itemize}

@@

\begin{itemize}
    \item Acknowledge the moral character of cryptography \cite{rogaway_moral_2015}
    \item Do the research
    \item Focus on principles \cite{levy_robinson_2018}
    \item Be clear on definitions \cite{varia_2018}, but don't expect govt to provide those (unlike
            \cite{abelson_2015}), and clearly define their interfaces with principles
            \cite{matyas_incommensurability_2018}
\end{itemize}
